A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$. Generally, the simulations closely resemble each other with the simulation in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) being the most identical. Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c). This is logical giving that the block mean values calculated for arithmetric mean is higher than that for harmonic mean. However, the important feature of the figures (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) is that they poorly represent the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$ . Fig.~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$. This inconsistence is with respect to this realization of the PDFCase. Hence, by elimination the SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)

>>>>

Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$. Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical. Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c)\red{(WHAT DO YOU MEAN W ``MORE INJECTION''? MASS FLOW RATE OF INJECTION (BC) WAS THE SAME FOR ALL CASES ...DO YOU MEAN THE DISPLACEMENT IN THE RHS QUADRANTS?)}. This is logical giving that the block mean values calculated for arithmetric mean is higher than that for harmonic mean. However, the important feature of the figures (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) is that they poorly represent the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$ . Fig.~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$. This inconsistence is with respect to this realization of the PDFCase. Hence, by elimination the SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
